\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-01-25 draft.tex
remove duplicate assumption ga_l_e and merged textual description

That is, even for the least favorable outcome of the lobbying process, the legislature will be at least slightly more protectionist than the executive. This assumption is not essential, but it matches well the empirical findings that politicians with larger constituencies are less sensitive to special interests, and it simplifies the analysis considerably, in particularly ensuring that trade agreement tariffs are less than trade war tariffs.

@@

Note that the legislature's best response functions (both for whether to break the agreement, and at what level to set the tariff if it does) will be affected by the shape of $\ga(e,\ve)$. I make the following assumptions on the weight on import-industry profits:

@@

Assumption~\ref{as:ga_l_e} ensures that $\tau^a < \tau^n$, and more generally, that the legislature's incentives are more closely aligned with the lobby's than are those of the executive. This is not essential but simplifies the analysis and matches well the empirical findings that politicians with larger constituencies are less sensitive to special interests (See Destler (2005) and footnote~\ref{fn:ga_l_e} above).

>>>>

That is, even for the least favorable outcome of the lobbying process, the legislature will be at least slightly more protectionist than the executive. This assumption is not essential, but it matches well the empirical findings that politicians with larger constituencies are less sensitive to special interests, and it simplifies the analysis considerably, in particular ensuring that trade agreement tariffs are less than trade war tariffs (See Destler (2005) and footnote~\ref{fn:ga_l_e} above).

@@

Note that the legislature's best response functions (both for whether to break the agreement, and at what level to set the tariff if it does) will be affected by the shape of $\ga(e,\ve)$. I make the following further assumptions on the weight on import-industry profits:

@@

%Assumption~\ref{as:ga_l_e} ensures that $\tau^a < \tau^n$, and more generally, that the legislature's incentives are more closely aligned with the lobby's than are those of the executive. This is not essential but simplifies the analysis and matches well the empirical findings that politicians with larger constituencies are less sensitive to special interests (See Destler (2005) and footnote~\ref{fn:ga_l_e} above).
